More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-12-18 2016-Weak-FH-Bisim/WeakBisim.tex
input variables
Lemma OT decomposition

The function
$\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$, and $iv(t)$ returns its input variables.
Action algebras can encode naturally usual point-to-point message passing calculi (using 
$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
communications.

@@

\begin{definition}[Sorts, Holes, Leaves of pNets]\label{def-sortholeleave}
  \begin{itemize}
  \item The sort of a pNet is its signature, i.e. the set of actions it can
perform, where each action signature is an action 
label plus the arity of the action. In the definition of sorts, we do not need to 
distinguish
input variables and we remove the
\emph{input marker} (?) of variables.
\[
\begin{array}{l}
\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
    J}\rangle} s'\in \to \} \\
\Sortop(\mylangle \set{\pNet}\!, %\pNet_i^{i\in I}, 
\set{\Sort},
\set{\symb{SV}}\myrangle)
=\{\alpha' |\, \SV{\set{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\}
\end{array}
\]

@@

\subsection{Composition properties}
\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction. Suppose $\gamma_{j_0}=[\beta_0..\beta_n]$
		 then there exist $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p= \beta_p\land \Pred_p) \qquad\text{and~}
\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}
\LUDO{A V2 by Ludo}

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall i \in [0\ldots n]	\,		
	P[Q]_{j_0}	\models		
\openrule
    {
       \set{(\beta^1_i)},\Pred^1_i,\Post^1_i   }
         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
~and~ $\forall i \in [0\ldots m] \, P[Q]_{j_0}	\models \openrule
         {
           \set{(\beta^3_i)},\Pred\,^3_i, \Post_i^3   }
         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
$\\
and $ P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
$ where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
\Post=\biguplus_{i=0}^{m}(\Post^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
$

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For  $\symb{OT}$ in the form: 
$P[Q]_{j_0}	\models		\openrule
    {
       \set{\beta}_p,\Pred_p,\Post_p   }
         {\ostate{s_p} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
We obtain:\\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_p}\!\!',  
				{\Post_p}\!\!'}
			{\ostate{(s_{p})_l^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{p}')_l^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
		%\[
		Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {\Pred_p''},  
				{\Post_p''}}
			{\ostate{(s_{p})_l^{l\in L_Q}} \OTarrow {\alpha_p}
				\ostate{({s_{(p+1)}})_l^{l\in L_Q}}}
		}%\]
		$\\
and  $\Pred_p \iff {\Pred_p}\!\!'
		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
		{\Post_p}\!\!''$ where ${\Post_p''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
\item For $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta},\Pred,\Post }
         {\ostate{s} \OTarrow {\alpha} \ostate{s'}}$\\
We obtain:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{s_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{s_l'^{\,l\in L_Q}}}
		}%\]
		$
		and  $\Pred \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude that we have:

\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

Where \TODO{I will add the rest}

Considering the set of $\symb{OT}_p$ of $Q$ such that $p \in [0\ldots m+n+1]$, at each time a single open transition moves.   So we have for each open transition:

\begin{mathpar}
Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

@@

By definition \ref{def:buildweakOT} we can conclude that we have for all $p\in[0\ldots n+m]$:

\begin{mathpar}
Q\models{\openrule
			{
				{\gamma_{pj}^{j\in J_p}}, {\Pred_p},  
				{\Post_p}'}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

Where $J_p = J\cap\Holes(Q)$, ???? $\gamma_{pj}=\vis{\beta_{pj}}$,\\  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p$

>>>>

The function
$\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$, and $iv(t)$ returns the name of its input variables (without the '?' marker).
Action algebras can encode naturally usual point-to-point message passing calculi (using 
$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
communications.

@@

\begin{definition}[Sorts, Holes, Leaves of pNets]\label{def-sortholeleave}
  \begin{itemize}
  \item The sort of a pNet is its signature, i.e. the set of actions it can
perform, where each action signature is an action 
label plus the arity of the action. In the definition of sorts, we do not need to 
distinguish
input variables and we remove the
\emph{input marker} (?) of variables.
\[
\begin{array}{l}
\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{?x \gets x| 
x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
    J}\rangle} s'\in \to \} \\
\Sortop(\mylangle \set{\pNet}\!, %\pNet_i^{i\in I}, 
\set{\Sort},
\set{\symb{SV}}\myrangle)
=\{\alpha' |\, \SV{\set{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\}
\end{array}
\]

@@

\subsection{Composition properties}
\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction. Suppose $\gamma_{j_0}=[\beta_0..\beta_n]$
		 then there exist $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p= \beta_p\land \Pred_p) \qquad\text{and~}
\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall i\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       \set{(\beta^1_i)},\Pred^1_i,\Post^1_i   }
         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
~and~ $\forall i \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           \set{(\beta^3_i)},\Pred\,^3_i, \Post_i^3   }
         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
$\\
and $ P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
$ where\\
$
s=s^1_0 \wedge s^1_{m_1}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s',
\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
\Post=\biguplus_{i=0}^{m_2}(\Post^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
$

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}	\models		\openrule
    {
       \set{\beta}_p,\Pred_p,\Post_p   }
         {\ostate{s_p} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_p}\!\!',  
				{\Post_p}\!\!'}
			{\ostate{(s_{p})_l^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{p}')_l^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \left\{
  \begin{array}{l}
		%\[
		Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
				or\\
		\openrule
         {
           (j\mapsto\tau)^{j\in L\cap\Holes(Q)},\True,\Id(s_{pl}^{l\in L_Q})}
         {s_{pl}^{l\in L_Q} \OTarrow {\tau} s_{pl}^{l\in L_Q}}

\end{array}
\right.$\\
such that  $\Pred_p \iff {\Pred_p}\!\!'
		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
\item Similarly, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta},\Pred,\Post }
         {\ostate{s} \OTarrow {\alpha} \ostate{s'}}$\\
We obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	 \left\{
  \begin{array}{l}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{s_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{s_l'^{\,l\in L_Q}}}
		}\\%\]
	or\\
		\openrule
         {
          (j\mapsto\tau)^{j\in L\cap\Holes(Q)},\True,\Id(s_{pl}^{l\in L_Q})}
         {s_{pl}^{l\in L_Q} \OTarrow {\tau} s_{pl}^{l\in L_Q}}

\end{array}
\right.	
		$
such that  $\Pred \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.
\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
Considering each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$, the set of open transition that moves at each time, i.e,  the open transition $\symb{OT}_p$ in the form:
\begin{mathpar}
Q\models{\openrule
			{
				(\beta_p)_j^{J_p}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

@@

By rule (\WTTrois)  we can conclude that for each $p\in S$ we have:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
such that $\gamma_p = \vis{\beta_p}$.\\
\TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\

For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ open transitions  $\symb{OT}_p$ s.t $p\in [0\ldots n]$.

Hence, we have forall $p\in [0\ldots n]$ :  
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p \quad$

\TODO{END???}
